% !Mode:: "TeX:UTF-8"
\begin{cabstract}
\TeX{}是一个排版系统，可以把文章做成书那种效果。因此\TeX{}非常适合用来写学术论文和书籍。\chdpaper{}是按照长安大学教务处对本科生毕业论文的要求设计和实现的\LaTeX{}模板，帮助长安大学的学生以专业排版水平来完成毕业论文。

本文既是\chdpaper{}使用手册也是范例，建议在使用\chdpaper{}之前阅读。

长安大学直属国家教育部，是教育部、交通运输部、住房和城乡建设部、国土资源部和陕西省政府共建的国家“211工程”重点建设大学，是国家“985工程”优势学科创新平台建设高校。

长安大学2000年是由始建于二十世纪50年代初的原西安公路交通大学、西安工程学院、西北建筑工程学院合并组建而成，是一所以工为主，理工结合，经济、管理、人文多种学科协调发展，以培养公路交通、国土资源与环境、建筑工程等专业人才为办学特色，在国内外有很大影响的高等学府。
\end{cabstract}
\ckeywords{长安大学，211，长大}
\newpage
\begin{eabstract}
\TeX{} is a typesetting system, it can make article as good as {\em published book}. Therefore, \TeX{} is very suitable for writing academic papers and books. \chdpaper{}is designed and implemented as a \LaTeX{} template to help studnets writing degree thesis in a professional typesetting, according to the requirements of Chang'an University.

This paper is \chdpaper{}user manual and also the sample document, it is better to be read before using \chdpaper{}.

Chang'an  University is a comprehensive national key university based in Xi'an, %
Shaanxi Province, China. It is under the dual supervision of the State Education Department, Ministry of land and resouces and the government of Shaanxi province, designated for Project 211, %
the plan for facilitating the development of Chinese higher education. %

CHD was founded in 2000 with the merger of original Xi'an Highway University,Xi'an College of Engineering,Northwestern Institude of Architectural Engineering which were founded at the beginning of the 50's in twentieth Century. %
To cultivate professional talents of highway traffic,land resoureces and environment,construction engineering as school characteristics,Chang'an  University is an institutions of higher learning that has great influnce in the domestic and foreign.
\end{eabstract}
\ekeywords{211, CHD, Chang'an  University}
\newpage